Fluid-mechanical erosion creates anisotropic porous media

### 2022-05-13 docs/PhysicsPaper/StokesErosion.tex
NM

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately solve the governing equations~\eqref{eqn:erosionModel} in
complex two-dimensional geometries, we reformulate the equations as a
BIE.  This has the advantage that only the one-dimensional boundary of
the domain must be discretized, and, with appropriate quadrature
formulas and fast summation methods, the result is a high-fidelity
numerical simulation with near-optimal computational complexity.

@@

%Note: If a larger value of $x_0$ is chosen, then one would be in effect averaging the porous-medium resistivity with the vanishing resistivity of the empty buffer region.

@@

Therefore we have the relationship
\begin{equation}
r \approx \frac{1}{4 U}  \, \FD \cdot \ex
\end{equation}

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{}
\includegraphics[width = 0.99 \textwidth]{./figs/figA.pdf}
\caption{caption}
\end{figure*}
%---------------------------------------------------------%

>>>>

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%

\vsp{2} \nick{Finished rewording up to here} \vsp{2}

To accurately solve the governing equations~\eqref{eqn:erosionModel} in
complex two-dimensional geometries, we reformulate the equations as a
BIE.  This has the advantage that only the one-dimensional boundary of
the domain must be discretized, and, with appropriate quadrature
formulas and fast summation methods, the result is a high-fidelity
numerical simulation with near-optimal computational complexity.

@@

Probably should just use
\begin{equation}
k = \frac{2U}{\pup - \pdn}
\end{equation}
%Note: If a larger value of $x_0$ is chosen, then one would be in effect averaging the porous-medium resistivity with the vanishing resistivity of the empty buffer region.

@@

Therefore we have the relationship
\begin{equation}
\label{ResistDrag}
1/k \approx \frac{1}{4 U}  \, \FD \cdot \ex
\end{equation}

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{}
\includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
\caption{A single simulation of porous-medium erosion. The initial configuration consists of 80 circular bodies of random size and position, as seen in Fig.~1? a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases. b) Resistance to flow can be characterized by either the inverse permeability $1/k$ or the cumulative drag, the two of which are related through \eqref{ResistDrag}. Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium. Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
}
\end{figure*}
%---------------------------------------------------------%
